### 2020-04-20 final_report/methodology.tex

The unsupervised setting can be viewed as an extension of this procedure.
Rather than fixing the training set $\mathcal{T}$ for the entire duration of
training, the points of evaluation $\{x^{(i)}\}_{i=1}^N$ that determine the set
are first initialised randomly, and continuously extended throughout training. This
permits the learning algorithm to motivate the choice of new points following the
evaluation of surrogates trained thus far by appropriately biasing the
proposal distribution, in order to better focus on problematic regions within
the domain.

>>>>

The unsupervised setting can be viewed as an extension of this method.
Rather than fixing the training set $\mathcal{T}$ for the entire duration of
training, multiple sets $\{\mathcal{T}_k\}_{k=0}^K$ are used, such that
$\mathcal{T}_{k-1}\subset\mathcal{T}_k$ for all $k$. The first set
$\mathcal{T}_0$ is initialised randomly to provide a \textit{burn-in}, and is
repeatedly extended in epochs. In each epoch, a new surrogate is trained on
$\mathcal{T}_k$ using the supervised learning procedure, and evaluated.
This permits the learning algorithm to motivate the choice of new points following the
evaluation of surrogates trained thus far by appropriately biasing a
proposal distribution, in order to focus on improvement of complex regions
within the domain.
